---
title: "Data_Replication_gpelose_Workbook1"
author: "Greg Pelose"
date: "12/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Getting data from excel into R
```{r}
install.packages("readxl")
```
```{r}
library(readxl)
```


Figure 1

```{r}
library(readxl)
library(ggplot2)
library(dplyr)
```

```{r}
Figure_1 <- read_excel("individual_project.xlsx", 
    sheet = "GP-Fig.1")
summary(Figure_1)
```

First I want to check and see if this checks out, then I will use ggplot to mimic the graph that they created

```{r}
boxplot(Figure_1, xlab="Plastic Type", ylab="no. plastic per polyp")
```

Questions about figure 1:
I cannot figure out how to get the A, A, B above the image
I cannot figure out how to change the values of the y-axis

Attempting to create in ggplot
```{r}
Plot_1 <-ggplot(Figure_1, aes(x=Figure_1$beads, Figure_1$fibers, Figure_1$Misc, y=???????))


```

Questioins:
How do I make this work

FIgure 2

```{r}
Figure_2 <- read_excel("individual_project.xlsx", 
    sheet = "GP-Fig.2")
summary(Figure_2)
names(Figure_2)
```
```{r}
top <- Figure_2$Top 
middle <- Figure_2$Middle
Bottom <- Figure_2$Bottom
top
```

```{r}
Sheet_2_Fig_2 <- read_excel("individual_project.xlsx", 
    sheet = "sheet 2 again")
summary("sheet 2 again")
names("Sheet 2 again")
```

```{r}
Plot_2 <- ggplot(Figure_2, aes(x=top, y=))
plot_2 + geom_bar()
```



#Figure 3

```{r}
Figure_3 <- read_excel("individual_project.xlsx", 
     sheet = "GP-Fig.3")
summary(Figure_3)
boxplot(Figure_3, ylab="particles consumed (mm^3)")
```


#Figure 4






#Figure 5

```{r}
Figure_5 <- read_excel("individual_project.xlsx", 
    sheet = "GP-Fig.5")
summary(Figure_5)
plot(Figure_5)
```


